Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-31 ms.tex
100 GHz quadrupole description

For \PLANCK~100 GHz, we found an additional low-order correction to be
necessary. Therefore, for 100 GHz, we performed a modified version of the 
Eqation \ref{equ:dip} fit, using the following model:

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_p + c + qQ_p
\end{equation}

% mention the special case of 100 GHz w/ quadrupole term !!!!!!
% do i need another equation ?

>>>>

For \PLANCK~100 GHz, we found an additional low-order correction to be
necessary (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we performed a 
modified version of the Equation \ref{equ:dip} fit, using the following model:

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_p + b + qQ_p
\end{equation}

We will refer to the additional term $qQ_p$ as the ``quadrupole correction''. 
The shape of the quadrupole template is given by:

\begin{equation}
Q_p = cos^2(\theta_p)
\end{equation}

Where $\theta_p$ is the angle of pixel $p$ relative to the Solar velocity 
vector. It is not clear physically why such a term should improve the 
correlation between $\mathcal{I}_{100}$ and $\mathcal{I}_{857}$. However, the 
scatter plots shown in Figure \ref{fig:quad} make it clear that such a term, 
with best-fit amplitude $q$=$-7.17$$\times$10$^{-6}$, dramatically improves the
quality of the linear correlation between the 100 GHz and 857 GHz channels. We 
tried re-running the fits at 143-545 GHz including the $Q_p$ quadrupole term, 
but in all cases found the best-fit quadrupole to be negligible, and yield no 
substantial tightening of the correlation versus 857 GHz.

% worth clarifying that, for quadrupole fit at 100 GHz, we still do the
% fit with uniform weights and iterative outlier rejection ?
